### 2015-11-05 section/5_exper.tex
test
shrinking

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
                         &      	   &                        & {\bf Root}   &          \\
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf Cause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         & N/A             & JS                     &  C-I         & B       \\
   Mozilla35294          & N/A             & C++                    &  C-L         & B        \\ 
   Mozilla477564         & N/A             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           & N/A             & Java                   &  C-I         & B  \\
   Apache37184           & N/A             & Java                   &  C-I         & M  \\
   Apache29742           & N/A             & Java                   &  C-L         & B \\ 
   Apache34464           & N/A             & Java                   &  C-L         & M  \\
   Apache47223           & N/A             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (N/A: we skip the size of benchmarks that are extracted from real-world applications.
  Root cause ``C-I'' is short for cross-iteration redundancy.
  Root cause ``C-L'' is short for cross-loop redundancy.
  C, B, M, and S represent different fix strategies, as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool, when applying to top 5 loops reported by 
    statistical performance diagnosis for each benchmark. `-' represents zero false positive.
    Other cells report real false positives and benign false positives, which is in the
    subscript.
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, 4 benchmarks contain loops that only generate side-effect
in the last iteration among their top 5 suspicious loops. However,
these loops are actually not inefficient because the portion of
resultless iterations is small.

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop, with and
    without optimizations. 
    Only results from non-extracted benchmarks are shown. 
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}

>>>>

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
                         &      	   &                        & {\bf Root}   &          \\
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf Cause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           &  -             & Java                   &  C-I         & B  \\
   Apache37184           &  -             & Java                   &  C-I         & M  \\
   Apache29742           &  -             & Java                   &  C-L         & B \\ 
   Apache34464           &  -             & Java                   &  C-L         & M  \\
   Apache47223           &  -             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (-: benchmarks extracted from real-world applications.
  ``C-I'': cross-iteration redundancy.
  ``C-L'': cross-loop redundancy.
  C, B, M, S: fix strategies as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool, when applying to top 5 loops reported by 
    statistical performance diagnosis for each benchmark. `-': no false positive. $x_y$: $x$ real false positives and $y$ benign ones.
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, 4 benchmarks contain loops that only generate side-effect
in the last iteration among their top 5 suspicious loops. However,
these loops are actually not inefficient because the portion of
resultless iterations is small. 
%TODO a table 6 was deleted from oopsla submission

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not conducted, as static analysis is sufficient.
  /: not applicable.}
  \label{tab:performance}
\end{table}

### 2015-11-05 section/6_related.tex
shrinking

Many dynamic and static analysis tools have been built to detect different
types of performance problems, such as 
run-time bloat~\cite{Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}, 
low-utility data structures~\cite{Xu:2010:FLD:1806596.1806617}, 
cacheable data~\cite{Cachetor}, false sharing in
multi-thread programs~\cite{Liu:2011:SPD:2048066.2048070},
inefficient nested loops~\cite{Alabama},
loops with unnecessary iterations~\cite{CARAMEL,IsilDillig.PLDI15},
input-dependent loops~\cite{xiao13:context}, and others. 
%Some static tools \cite{PerfBug} identify performance defects that violate
%specific efficiency rules, often related to API usage.

>>>>

Many dynamic and static analysis tools have been built to detect different
types of performance problems, such as 
run-time bloat~\cite{Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}, 
low-utility data structures~\cite{Xu:2010:FLD:1806596.1806617}, 
cacheable data~\cite{Cachetor}, false sharing in
multi-thread programs~\cite{Liu:2011:SPD:2048066.2048070},
inefficient nested loops~\cite{Alabama},
loops with unnecessary iterations~\cite{CARAMEL,IsilDillig.PLDI15},
input-dependent loops~\cite{xiao13:context}. 
%Some static tools \cite{PerfBug} identify performance defects that violate
%specific efficiency rules, often related to API usage.
